Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-10 Manuscript.qmd
Update intro paragraph

  | This study contributes to a more nuanced understanding of LGBTQ+ individuals' diverse needs and experiences with queer media representation, which has significant implications for media producers, mental health professionals, and LGBTQ+ advocacy groups in fostering more positive and inclusive media representations for the LGBTQ+ community.
keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
bibliography: References.bib
format:
  apaquarto-pdf:
    documentmode: man
    indent: true
    include-in-header: 
      text: |
        \usepackage{setspace}
        \linespread{2}
---

>>>>

  | This study contributes to a more nuanced understanding of LGBTQ+ individuals' diverse needs and experiences with queer media representation, which has significant implications for media producers, mental health professionals, and LGBTQ+ advocacy groups in fostering more positive and inclusive media representations for the LGBTQ+ community.
keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
format:
  apaquarto-pdf:
    csl: apa.csl
    documentmode: man
    indent: true
    include-in-header: 
      text: |
        \usepackage{setspace}
        \linespread{2}
bibliography: References.bib
---
Since the Stonewall riots, queer characters have flourished in the mass media, reaching their peak in the information era. As the primary audience for queer media characters, the LGBTQ+ community is claimed to be both positively and negatively impacted by these characters [e.g., @craig_media:_2015;@nolke_making_2018]. While queer characters can favorably impact LGBTQ+ individuals’ identity development and self-esteem, stereotypical representations that lack intersectionality may result in stigmatization and negative mental outcomes. Nevertheless, few studies have compared queer characters’ impacts on different LGBTQ+ subgroups, probably because they ignored the emergence of more marginal groups (e.g., asexual). Additionally, no established instruments have explored how perceived character authenticity or intersectionality may contribute to different psychological well-being outcomes. Knowing LGBTQ+ individuals' diverse needs and experiences with queer media representation is important as it can call for more diverse and inclusive queer media representations. Through developing a reliable instrument on queer media characters’ psychological impacts and conducting worldwide data collection across different LGBTQ+ generations, this study aimed to contribute to a deeper understanding of queer characters’ psychological impacts on different LGBTQ+ groups.

# Literature Review

##
